---
title: "Mixture and Convolution"
author: "Xiaoqian Wang"
date: "`r Sys.Date()`"
output: 
  html_document:
    keep_md: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Mixture and Convolution

Let $X_{1}, \ldots, X_{N}$ denote random variables from the $N$ component distributions, $X_{i} \sim f_i$ for $(i=1,\ldots,N)$.

- **A mixture distribution** has a density which is a weighted sum of a set of probability densities.

$$
f_{c}(x) = \sum_{i=1}^{N} w_{i} f_{i}(x).
$$

- **A convolution** gives a distribution of a random variable which is a sum of a set of random variables.

$$
f_w (x) = f_{x_1 + \ldots + x_N} (x) = (f_1 \cdot f_2 \cdot \ldots \cdot f_N)(x).
$$

- An example: $X_1 \sim N(3700, 80)$ and $X_2 \sim N(3900, 120)$ with equal weights.

```{r DiscreteExample, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=6}
x <- seq(3200,4300,1)
par(mfrow=c(2,1))
plot(x, dnorm(x, 3700, 80), type = "l", col = "darkblue", lwd = 2,
     ylim = c(0,0.006), ylab = "", main = "Convolution")
lines(x, dnorm(x, 3900, 120), col = "darkred", lwd = 2)
lines(x, dnorm(x, 3800, sqrt(5200)), col = "black", lwd = 3)
plot(x, dnorm(x, 3700, 80), type = "l", col = "darkblue", lwd = 2, 
     ylim = c(0,0.006), ylab = "", main = "Mixture")
lines(x, dnorm(x, 3900, 120), col = "darkred", lwd = 2)
lines(x, 0.5*dnorm(x, 3700, 80)+0.5*dnorm(x, 3900, 120), col = "black", lwd = 3)
par(mfrow=c(1,1))
```

- The sum of two jointly normally distributed random variables, each with different means and variances, will still have a normal distribution.

- A mixture density created as a mixture of two normal distributions with different means will have two peaks provided that the two means are far enough apart, showing that this distribution is radically different from a normal distribution.

