\documentclass[a4paper,11pt]{article}

%%%%%%%%%%%%%%%%%% Non-Latin Languages Support %%%%%%%%%%%%%%%%%%%%%%%
% \usepackage[adobefonts,nocap]{ctex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[twoside]{geometry}
\geometry{verbose,tmargin=2.0cm,bmargin=5.5cm,lmargin=2.0cm,rmargin=2.0cm}
% \usepackage[raggedright]{titlesec}

\usepackage{graphicx}
\usepackage[unicode=true]{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue}

\usepackage{multirow}

%% Line spacing
\usepackage{setspace}
\onehalfspace

%% Fancy symbols
\usepackage{marvosym}


%% Fonts
\usepackage[ugaramond]{mathdesign}
% \usepackage{inconsolata}

%% Fancy header and footer
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}

\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.4pt}

\fancyfoot[L]{ \texttt{School of Economics and Management\\ Beihang University\\ 37 Xueyuan Road, Haidian District, 100083 Beijing, China}}

\fancyfoot[C]{\vspace{2.0cm} \thepage~/~\pageref{LastPage}}

\fancyfoot[R]{\texttt{https://sem.buaa.edu.cn\\ https://buaa.edu.cn\\}}


\begin{document} \thispagestyle{fancy}

\begin{tabular}{ll}
  \multirow{7}{*}{\hspace{4cm}\hspace{0.18\textwidth}}
  & Yanfei Kang, Ph.D. \\
  & School of Economics and Management \\
  & Beihang University\\
  & 100083 Beijing, China\\
  & \Email~\texttt{yanfeikang@buaa.edu.cn} \\
  & \Pointinghand~\texttt{https://yanfei.site/}\\
  & \\
  & \today
\end{tabular}

\vspace{1.5cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent Dear Editor,
\vspace{1cm}

Please find attached the manuscript entitled ``Forecast combinations: an over 50-year review'' by Xiaoqian Wang, Rob J Hyndman, Feng Li and Yanfei Kang, which we wish to submit for publication as a regular review article in \emph{International Journal of Forecasting}. No conflict of interest exits in the submission of this manuscript, and the manuscript is approved by all authors for publication. We confirm that the work is original research that has not been published previously, and not under consideration for publication elsewhere.

In this paper, we present an up-to-date modern review of the literature on forecast combinations over the past five decades since the seminal work of Bates and Granger (1969). We cover a wide variety of forecast combination methods for both point forecasts and probabilistic forecasts, contrasting them and highlighting how various related ideas have developed in parallel.  Some important issues concerning the utility of forecast combinations are also surveyed. We finally conclude with current research gaps and potential insights for future research.

We hope that the manuscript meets the standards of your journal. Thank you for your
consideration.

\vspace{1.5cm}

\noindent Sincerely,
\bigskip

\noindent Yanfei Kang

\end{document}